Model-Based CubeSat Flight-Software Architecture using a Docs-as-Code approach

### 2022-12-03 research/manuscript-example/manuscript.tex
Added OML references and paragraph

\author{First A. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for first author.} and Second B. Author Jr.\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for second author.}}
\affil{Business or Academic Affiliation 1, City, State, Zip Code}
\author{Third C. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for third author.}}
\affil{Business or Academic Affiliation 2, City, Province, Zip Code, Country}
\author{Fourth D. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for fourth author (etc.).}}
\affil{Business or Academic Affiliation 2, City, State, Zip Code}

@@

{\renewcommand\arraystretch{1.0}
\noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
$1U$ 1-Unit \\
$3U$ 3-Unit \\
$BOM$  & Bill of Materials \\
$ConOps$  & Concept of Operations \\
$DOF$  & Distributed OSHW Framework  \\
$m30ml$  & mach30 modeling language \\
$MBSE$ &    model-based systems engineering  \\
$ODU$& Old Dominion University \\
$OML$  & Ontological Modeling Language \\
$OSHW$ & Open Source Hardware \\
$USCGA$ & United Stated Coast Guard Academy \\
$WFF$   & Wallops Flight Facility  
\end{longtable*}}

@@

>>>>

\author{Sean Marquez and Kevin Chiu}
\affil{Old Dominion University, Norfolk, VA, 23529}
\author{Sharan Asundi, Ph.D. \\footnote{Assistant Professor, Department of Mechanical & Aerospace Engineering, Old Dominion University}}
\affil{Old Dominion University, Norfolk, VA, 23529}

@@

{\renewcommand\arraystretch{1.0}
\noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
$1U$ 1-Unit \\
$3U$ 3-Unit \\
$BOM$  & Bill of Materials \\
$ConOps$  & Concept of Operations \\
$DOF$  & Distributed OSHW Framework  \\
$m30ml$  & mach30 modeling language \\
$MBSE$ &    model-based systems engineering  \\
$ODU$& Old Dominion University \\
$OML$  & Ontological Modeling Language \\
$OSHW$ & Open Source Hardware \\
$OWL2$ & Web Ontology Language 2 \\
$SWRL$ & Semantic Web Rule Language \\
$USCGA$ & United Stated Coast Guard Academy \\
$WFF$   & Wallops Flight Facility  
\end{longtable*}}

@@

OML is a language that "enables defining systems engineering vocabularies and using them to describe systems \cite:{oml_language}." OML, inspired by Web Ontology Language 2 (OWL2) and the Semantic Web Rule Language (SWRL), is meant to be a more gentler and more disciplined method of afformentioned standard for use in systems engineering \cite:{oml_language}. OML was created in part since OWL2 does not conform easily to individual modelling rules without tooling support; OML is a tool to improve speed of modeling and the quality of models while in a more concise and human-friendly high-level external representation \cite:{oml_origin_and_rationale}. Thus, OML served as a useful basis to create the m30ml since both run on similar philosophies to simplify usage for the end user.
